---
title: "Data Collection"
author: "Niklas"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(visdat)
```

# Load Data

```{r}
df <- read_csv("data/collection/dat_col_v3.csv")

double_eids <- df %>% 
  group_by(eid) %>% 
  count() %>% 
  filter(n > 1)

df <- df %>% 
  slice(-c(1:2)) %>% 
  type_convert() %>% 
  filter(eid != "FFE1DC0E-FF7D-479D-B4BB-A1E14E4AEA88") %>% # test eid
  slice(1, .by = eid) %>% 
  mutate(quality_questions = ifelse(StartDate < "2023-07-24 11:42:00 UTC", "old", "new"))
```

```{r}
df_ongoing <- read_csv("data/collection/dat_col_unfinished_v3.csv")

df_ongoing <- df_ongoing %>% 
  slice(-c(1:2)) %>% 
  type_convert() %>% 
  filter(eid != "FFE1DC0E-FF7D-479D-B4BB-A1E14E4AEA88") %>% # test eid
  slice(1, .by = eid) %>% 
  mutate(quality_questions = ifelse(StartDate < "2023-07-24 11:42:00 UTC", "old", "new"))
```

# Visualize Missing

```{r}
df %>% 
  vis_miss()
```

# Which Redirect Do People Get

Before changing up the quality questions:

```{r}
outs <- df %>% 
  filter(quality_questions == "old") %>% 
  mutate(finished = !is.na(comments),
         so_consent = consent != 1,
         so_age = age < 18 & age > 0,
         so_language = native_language == 3,
         so_social_media_use = social_media_use > 8,
         bq_q1 = compr_question_2_1 != 3,
         bq_q2 = compr_question_2_2 != 1) %>% 
  filter(!is.na(eid)) %>% 
  select(eid, quality_questions, starts_with("so_"), starts_with("bq"), finished)
```

After changing up the quality questions:

```{r}
outs <- df %>% 
  filter(quality_questions == "new") %>% 
  mutate(finished = !is.na(comments),
         so_consent = consent != 1,
         so_age = age < 18 & age > 0,
         so_language = native_language == 3,
         so_social_media_use = social_media_use > 8,
         bq_q1 = compr_question_2_1 != 2,
         bq_q2 = compr_question_2_2 != 1) %>% 
  filter(!is.na(eid)) %>% 
  select(eid, quality_questions, starts_with("so_"), starts_with("bq"), finished) %>% 
  rbind(outs) %>% 
  arrange(desc(so_consent), desc(so_age), desc(so_language))
```

```{r}
outs
```

## Sanity Check

For old, both quality questions have to be answered correctly to continue.

Code below should reult in nrow() == 0

```{r}
outs %>% 
  filter(quality_questions == "old") %>% 
  filter((bq_q1 == TRUE | bq_q2 == TRUE) & finished == TRUE)
```

For new, only one quality question has to be answered correctly to continue.

```{r}
outs %>% 
  filter(quality_questions == "new") %>% 
  filter((bq_q1 == TRUE | bq_q2 == TRUE) & finished == TRUE)
```

```{r}
outs %>% 
  filter(quality_questions == "new") %>% 
  filter((bq_q1 == TRUE & bq_q2 == TRUE) & finished == TRUE)
```

## Add Bad Quality Variable

```{r}
outs <- outs %>% 
  mutate(bad_quality = case_when(quality_questions == "old" & (bq_q1 == TRUE | bq_q2 == TRUE) ~ TRUE,
                                 quality_questions == "new" & (bq_q1 == TRUE & bq_q2 == TRUE) ~ TRUE,
                                 .default = FALSE))
```


```{r}
df <- df %>%
  left_join(select(outs, eid, bad_quality))
```

```{r}
df_ongoing <- df_ongoing %>%
  left_join(select(outs, eid, bad_quality))
```

## Overview

```{r}
outs %>%
  summarise(across(-c(eid, quality_questions), \(x) sum(x, na.rm = TRUE)))
```

```{r}
outs %>% 
  group_by(quality_questions) %>% 
  summarise(across(-eid, \(x) sum(x, na.rm = TRUE)))
```

```{r}
outs %>% 
  summarise(across(-c(eid, quality_questions), \(x) sum(x, na.rm = TRUE)/nrow(outs)))
```

```{r}
outs %>% 
  filter(quality_questions == "old") %>% 
  summarise(across(-c(eid, quality_questions), \(x) sum(x, na.rm = TRUE)/nrow(.)))
```

```{r}
outs %>% 
  filter(quality_questions == "new") %>% 
  summarise(across(-c(eid, quality_questions), \(x) sum(x, na.rm = TRUE)/nrow(.)))
```

Screenout + Complete

```{r}
outs %>% 
  filter(so_social_media_use == TRUE |
           so_language == TRUE |
           so_consent == TRUE |
           finished == TRUE) %>% 
  nrow()/nrow(outs)
```

## Comments

```{r}
df$comments %>% 
  table()
```

```{r}
df_finished <- df  %>%
  filter(!is.na(comments))
```

```{r}
df_finished %>% 
  summarise(time = median(EndDate - StartDate))
```

```{r}
table(df_finished$gender)
```

```{r}
df_finished %>% 
  ggplot(aes(age)) +
  geom_bar()
```

```{r}
df_finished <- df_finished %>% 
  mutate(age_category = case_when(age < 34 ~ "under_34",
                                  age >= 34 & age < 50 ~ "under_50",
                                  age >= 50 & age < 65 ~ "under_65",
                                  age >= 65 ~ "under_99",
                                  .default = NA))
```

```{r}
df_finished %>% 
  mutate(gender = ifelse(gender == 1, "m", "w")) %>% 
  count(age_category, gender)
```

# Where Drop Out?

## After Quality Questions

```{r}
df_after_bq <- df_ongoing %>% 
  filter(consent == 1 &
           native_language != 3 &
           social_media_use <= 8 & 
           bad_quality == FALSE)
```

```{r}
if (nrow(df_after_bq) > 0) {
  df_after_bq[, grep("compr_question_2_2", colnames(df_after_bq)):ncol(df_after_bq)] %>% 
  vis_miss()
} else {
  
  print("Keine nach Quality")
  
}
```

## Before Quality Questions

```{r}
df_before_bq <- df_ongoing %>% 
  filter(!(eid %in% df_after_bq$eid))
```

```{r}
if (nrow(df_before_bq) > 0) {
  df_before_bq[, 1:grep("compr_question_2_2", colnames(df_before_bq))] %>% 
  vis_miss()
}
```

```{r}
sum(df_ongoing$eid %in% df$eid)
```

## Relative Amount Drop Outs

```{r}
(nrow(df_ongoing) - sum(df_ongoing$eid %in% df$eid))/(nrow(df_ongoing) - sum(df_ongoing$eid %in% df$eid) + nrow(df))
```

# Feedback Kinau

```{r}
last_obs <- df %>% 
  arrange(desc(EndDate)) %>% 
  slice(1) %>% 
  pull(EndDate) %>% 
  str_replace_all(" ", "_") %>% 
  str_replace_all(":", "-")
```

```{r}
outs %>%
  summarise(across(-c(eid, quality_questions), \(x) sum(x, na.rm = TRUE))) %>% 
  write_csv(file = paste0("data/collection/outs_", last_obs, ".csv"))
```

```{r}
df_finished %>% 
  mutate(gender = ifelse(gender == 1, "m", "w")) %>% 
  count(age_category, gender) %>% 
  write_csv(file = paste0("data/collection/quotas_", last_obs, ".csv"))
```

```{r}
df_finished %>% 
  select(eid) %>% 
  write_csv(file = paste0("data/collection/eids_finished_", Sys.Date(), ".csv"))
```

